% ============================================================
% AWARDS — full (11 active entries)
% Source: section_awards.tex (deprecated)
% Commented-out entries from original are preserved below.
% ============================================================

\subsection{SELECTED AWARDS}
\vspace{2pt}

\noindent
\begin{tabularx}{\textwidth}{@{}lX@{}}
2025 & Excellence in Research Award, School of Computing and Information Systems, University of Melbourne. \\[2pt]
2024 & Winning team at the ACM/IEEE International Conference in Human-Robot Interaction (HRI2024) Robot Competition. \\[2pt]
2023 & \href{https://www.womeninai.co/waiawards2023apac}{Women in AI Award -- Education in APAC Region}. \\[2pt]
2021 & GROW Award -- UNSW Faculty of Engineering 2021 -- 20k AUD Early Career Research Award. \\[2pt]
2020 & UNSW Faculty of Engineering 2020 Award for the category Equity, Diversity and Inclusion. \\[2pt]
2020 & \href{http://humanrobotinteraction.org/2020/best-paper-awards/}{Best Demo Award for our paper CoWriting Kazakh -- Learning a New Script with a Robot Demonstration}. \\[2pt]
2019 & \href{http://ilt.nutn.edu.tw/icce2019/04_Best\%20Reviewer\%20Award.html}{Best Reviewer Award for the 27th International Conference on Computers in Education}. \\[2pt]
2018 & Best Paper Award: Honorable Mention. ACM Interaction Design and Children Conference (IDC'18), Trondheim, Norway. \\[2pt]
2017 & Best Paper Award: ACM Human-robot Interaction Conference (HRI'17), Vienna, Austria. \\[2pt]
2015 & Winner of the \href{https://hal.inria.fr/hal-01208300/document}{Social Touch Challenge} at International Conference on Multimodal Interaction (ICMI). Nov.\ 2015. \\[2pt]
2015 & Best Paper Award: Honorable Mention, ACM Human-robot Interaction Conference 2015 (HRI), Portland, USA. \\
\end{tabularx}

% (was commented out in original:)
%2022 & Southern Cross Visiting Fellowships -- CIS University of Melbourne. \\  % (was commented out in original)
%2016 & Qualification for a position as an assistant professor in Computer Sciences, by the French Ministry of Research and Education (Ref: 16227283862), From 29/01/2016. \\  % (was commented out in original)
%2015 & HRI Pioneers: International Conference on Human Robot Interaction 2015 (HRI), Portland, USA. \\  % (was commented out in original)
