% ============================================================
% PROJECTS — short (7 active entries)
% Source: section_projects_short.tex (deprecated)
% Commented-out entries from original are preserved below.
% ============================================================

\subsection{SELECTED RESEARCH PROJECTS}
\vspace{2pt}

\noindent
\begin{tabularx}{\textwidth}{@{}lX@{}}
2026--2030 & \textbf{Balancing Autonomy and Control in Interactive Social Agent Design} \\
           & \emph{Proposal author, Lead CI} \\
           & This ARC Future Fellowship develops frameworks for designing AI-driven social agents that balance autonomy with user control. It introduces adaptive control and feedback systems for socially aligned, safe, and inclusive human-AI interactions across education, aged care, and remote collaboration contexts. \\
           & \textit{Lead PI, Australian Research Council, FT250100459, 4 Years Fellowship} \\[3pt]

2026--2033 & \textbf{ARC Centre of Excellence for Quality Work in a Digital Age (Qwida)} \\
           & \emph{Chief Investigator, Proposal co-author} \\
           & The Centre is composed of 7 Australian universities. The Centre's vision is to enable a future where workers and organisations are empowered by technology, rather than beholden to it. \\
           & \textit{University of Melbourne, 94M AUD} \\[3pt]

2021--2024 & \textbf{Human-Centered Robot Learning} \\
           & \emph{Proposal author, Lead CI} \\
           & This project is funded by the ARC. The goal of the project is to investigate novel interaction methods to allow novices to teach robots basic tasks for at home deployment. \\
           & \textit{440k AUD, 3 Years Project, ARC DECRA} \\[3pt]

2019--2022 & \textbf{IReCheck} \\
           & \emph{Proposal co-author, International Partner} \\
           & The IReCheck project, is funded by the Swiss NSF and the French ANR. The goal of the project is to investigate social and task adaptation in a Learning by Teaching task with Typically Developed children and children with Neuro-Developmental Disorders. \\
           & \textit{CHILI EPFL, 490k CHF, 3 Years Project} \\[3pt]

2018--2022 & \textbf{Animatas} \\
           & \emph{Proposal co-author, International Partner} \quad \href{http://animatas.eu}{animatas.eu} \\
           & The Animatas project, is a Horizon EU MSCA ITN that aims to explore the use of virtual and robotic agents in educational context. \\
           & \textit{CHILI EPFL, 759k CHF, 3 Years Project, 3 PhD Students} \\[3pt]

2018--2020 & \textbf{Cowriting Kazakh} \\
           & \emph{Principal Coordinator, Proposal co-author} \quad \href{https://chili.epfl.ch/cowriter}{chili.epfl.ch/cowriter} \\
           & Using social robots to help children learn handwriting and transition from Cyrillic to Roman alphabet, in Kazakhstan. \\
           & \textit{CHILI EPFL, 10k CHF, 2 Years Project, Nazarbayev University} \\[3pt]

2015--2019 & \textbf{Cellulo -- Tangible Haptic Robots for Education and Rehabilitation} \\
           & \emph{Project manager, Proposal co-author} \quad \href{http://chili.epfl.ch/cellulo}{chili.epfl.ch/cellulo} \\
           & The Cellulo project, funded by the NCCR Robotics (Swiss NSF), aims to design and propose new use of tangible swarm robots in education. \\
           & \textit{CHILI/MOBOTS EPFL, 1M CHF, 2 PhD + 1 Postdoc} \\
\end{tabularx}

% (was commented out in original projects_short:)
%2024       & \textbf{Trust in Adaptive Robot Autonomy based on Human's Mental State} \\
%           & \emph{Project Lead, Proposal co-author} \\
%           & This project aims to develop user-centered tools that enhance the interaction between workers and robotic systems by adjusting the level of autonomy of the robot in response to the human's mental state. \\
%           & \textit{University of Melbourne, 30k AUD} \\  % (was commented out in original)
%
%2018--2020 & \textbf{Find your voice!} \\
%           & \emph{Local Coordinator, Proposal co-author} \\
%           & The project aims to help children who struggle to find their voice in social situations. \\
%           & \textit{CHILI EPFL/UNSW, 15k CHF, Partners: UCL UK, University of Sussex, UC Irvine} \\  % (was commented out in original)
%
%2024--2025 & \textbf{A3: An Automatic Academic Advisor Tool} \\
%           & \emph{Project Lead, Proposal co-author} \\
%           & The project aims to design and develop a solution for visualisation of the curriculum. \\
%           & \textit{LTI 2023, University of Melbourne, 30k AUD} \\  % (was commented out in original)
