% ============================================================
% PUBLICATIONS — full manual list
% Source: section_publications.tex (deprecated)
%
% Organised by category; most recent first within each category.
% bib/references.bib contains the same entries in BibTeX format
% for export / future migration.
% ============================================================

% ---- Peer-reviewed Journal Publications ----
\subsection{PEER-REVIEWED SCIENTIFIC JOURNAL PUBLICATIONS}
\vspace{2pt}

\begin{itemize}[nosep]
    \renewcommand\labelitemi{$\bullet$}

    \item Shen, Y., \& \textbf{Johal, W.} (2025). TED-culture: culturally inclusive co-speech gesture generation for embodied social agents. \textit{Frontiers in Robotics and AI}, 12, 1546765.

    \item Tozadore, D., Nasir, J., \textbf{Johal, W.}, \& Neumann, M.\ M. (2025). Advances in robots for learning. \textit{Frontiers in Robotics and AI}, 12, 1584122.

    \item Parker, S.K., Ballard, T., Billinghurst, M., Collins, C., Dollard, M., Griffin, M.A., \textbf{Johal, W}., Jorritsma, K., Kowalkiewicz, M., Kyndt, E.\ and Lusher, D. (2025). Quality work in the future: New directions via a co-evolving sociotechnical systems perspective. \textit{Australian Journal of Management}, p.03128962251331813.

    \item Pan, J., Eden, J., Oetomo, D., \& \textbf{Johal, W.} (2024). Effects of Shared Control on Cognitive Load and Trust in Teleoperated Trajectory Tracking. \textit{IEEE Robotics and Automation Letters}, 9(6), 5863--5870.

    \item Gargot, T., Archambault, D., Chetouani, M., Cohen, D., \textbf{Johal, W.}, \& Anzalone, S.\ M. (2022). Automatic assessment of motor impairments in Autism Spectrum Disorders: A systematic review. \textit{Cognitive Computation}, 14, 624--659.

    \item \textbf{Johal, W.}, Belpaeme, T., \& Chetouani, M. (2022). Robots for learning. \textit{Frontiers in Robotics and AI}, 9, 1050658.

    \item \textbf{Johal, W.}, Gatos, D., Yantac, A.\ E., \& Obaid, M. (2022). Envisioning social drones in education. \textit{Frontiers in Robotics and AI}, 9, 666736.

    \item Olsen, J.\ K., Ozgur, A.\ G., Sharma, K., \& \textbf{Johal, W.} (2022). Leveraging eye tracking to understand children's attention during game-based, tangible robotics activities. \textit{International Journal of Child-Computer Interaction}, 31, 100447.

    \item Chalapathi G., Chamola, V., \textbf{Johal, W}., Aryal, J., \& Buyya, R. (2022). Energy and latency aware mobile task assignment for green cloudlets. \textit{Simulation Modelling Practice and Theory}, 118, 102531.

    \item Ozgur, A.\ G., Wessel, M.\ J., Olsen, J.\ K., Cadic-Melchior, A.\ G., Zufferey, V., \textbf{Johal, W.}, Dominijanni, G., Turlan, J.-L., Mühl, A., Bruno, B., Vuadens, P., Dillenbourg, P., \& Hummel, F.\ C. (2022). The effect of gamified robot-enhanced training on motor performance in chronic stroke survivors. \textit{Heliyon}, 8(11).

    \item Amirova, A., Rakhymbayeva, N., Yadollahi, E., Sandygulova, A., \& \textbf{Johal, W.} (2021). 10 Years of Human-NAO Interaction Research: A Scoping Review. \textit{Frontiers in Robotics and AI}, 8, 744526.

    \item Asselborn, T., \textbf{Johal, W.,} Tleubayev, B., Zhexenova, Z., Dillenbourg, P., McBride, C., \& Sandygulova, A. (2021). The transferability of handwriting skills: From the Cyrillic to the Latin alphabet. \textit{npj Science of Learning}, 6(1), 6.

    \item Gargot, T., Asselborn, T., Zammouri, I., Brunelle, J., \textbf{Johal, W.}, Dillenbourg, P., Archambault, D., Chetouani, M., Cohen, D., \& Anzalone, S.\ M. (2021). ``It Is Not the Robot Who Learns, It Is Me.'' Treating Severe Dysgraphia Using Child--Robot Interaction. \textit{Frontiers in Psychiatry}, 5.

    \item Zhexenova, Z., Amirova, A., Abdikarimova, M., Kudaibergenov, K., Baimakhan, N., Tleubayev, B., Asselborn, T., \textbf{Johal, W.}, Dillenbourg, P., CohenMiller, A., \& Sandygulova, A. (2020). A Comparison of Social Robot to Tablet and Teacher in a New Script Learning Context. \textit{Frontiers in Robotics and AI}, 7, 99.

    \item \textbf{Johal, W.} (2020). Research Trends in Social Robots for Learning. \textit{Current Robotics Reports}, 1--9.

    \item Guneysu O., A., Özgür, A., Asselborn, T., \textbf{Johal, W.}, Yadollahi, E., Bruno, B., Skweres, M., \& Dillenbourg, P. (2020). Iterative Design and Evaluation of a Tangible Robot-Assisted Handwriting Activity for Special Education. \textit{Frontiers in Robotics and AI}, 7.

    \item Guneysu O., A., Wessel, M.\ J., Olsen, J.\ K., \textbf{Johal, W.}, Özgür, A., Hummel, F.\ C., \& Dillenbourg, P. (2020). Gamified Motor Training with Tangible Robots in Older Adults: A Feasibility Study and Comparison with Young. \textit{Frontiers in Aging Neuroscience}, 12.

    \item Gargot, T., Asselborn, T., Pellerin, H., Zammouri, I., M.\ Anzalone, S., Casteran, L., \textbf{Johal, W.}, Dillenbourg, P., Cohen, D., \& Jolly, C. (2020). Acquisition of handwriting in children with and without dysgraphia: A computational approach. \textit{PLOS ONE}, 15(9), e0237575.

    \item Asselborn, T., Gargot, T., Kidzinski, L., \textbf{Johal, W.}, Cohen, D., Jolly, C., \& Dillenbourg, P. (2019). Reply: Limitations in the creation of an automatic diagnosis tool for dysgraphia. \textit{npj Digital Medicine}, 2(1), 37.

    \item Asselborn, T., Sharma, K., \textbf{Johal, W.}, \& Dillenbourg, P. (2019). Bridging Multilevel Time Scales in HRI: An Analysis Framework. \textit{ACM Transactions on Human-Robot Interaction}, 8(3), 17.

    \item Asselborn, T., Gargot, T., Kidzinski, Ł., \textbf{Johal, W}., Cohen, D., Jolly, C., \& Dillenbourg, P. (2018). Automated human-level diagnosis of dysgraphia using a consumer tablet. \textit{npj Digital Medicine}, 1(1), 42.

    \item \textbf{Johal W.}, Castellano G., Fumihide T., Okida S. Robots for Learning. \textit{International Journal of Social Robotics}, 2018.

    \item Mondada F., Bonnet E., Davrajh S., \textbf{Johal W.}\ and Stopforth R. R2T2: Robotics to Integrate Educational Efforts in South Africa and Europe. \textit{International Journal of Advanced Robotic Systems}, 2016.

    \item Vaufreydaz D., \textbf{Benkaouar (Johal) W.}, and Combe C. Starting engagement detection towards a companion robot using multimodal features. \textit{Robotics and Autonomous Systems}, January 2016.
\end{itemize}

\vspace{0.1in}

% ---- Peer-reviewed International Conference Publications ----
\subsection{PEER-REVIEWED INTERNATIONAL CONFERENCE PUBLICATIONS}
\vspace{2pt}

\begin{itemize}[nosep]
    \renewcommand\labelitemi{$\bullet$}


  \item Bilal, M., Ratnayake, T. S., Chacon, D. A., Lipovetzky, N., Oetomo, D., \& \textbf{Johal, W.} (2026). Design and evaluation of AR-based real-time feedback system for kinesthetic robot teaching. In Proceedings of the Designing Interactive Systems Conference (DIS '26). ACM. https://doi.org/10.1145/3800645.3812951 \faMedal

    \item Wong, E., Paxton, F., Pook, H., Howe, J., Grønbæk, J. E., \textbf{Johal, W.}, Velloso, E., \& Vetere, F. (2026). Systemic futures: Integrating critical speculation and systemic design pragmatism. DIS '26: Proceedings of the ACM Conference on Designing Interactive Systems, Singapore. https://doi.org/10.1145/3800645.3812901 \faMedal

    \item Tabatabaei, R., Kostakos, V., \& \textbf{Johal, W.} (2026). Oops, I Did It Again (But I Know It): Robot Failure Consistency and Awareness in Human-Robot Collaboration. \textit{Proceedings of the 2026 CHI Conference on Human Factors in Computing Systems}. ACM. \faMedal

    \item Zhang, J., \textbf{Johal, W.}, \& Knibbe, J. (2026). Modelling Visuo-Haptic Perception Change in Size Estimation Tasks. \textit{Proceedings of the 2026 CHI Conference on Human Factors in Computing Systems}. ACM.

    \item Bilal, M., Chacon, D.A., Lipovetzky, N., Oetomo, D., \& \textbf{Johal, W.} (2026). Investigating the Impact of Robot Degree of Redundancy on Learning from Demonstration. \textit{Proceedings of the 2026 ACM/IEEE International Conference on Human-Robot Interaction}. ACM/IEEE.

    \item Schömbs, S., Zhang, Y., Goncalves, J., \& \textbf{Johal, W.} (2025). From Conversation to Orchestration: HCI Challenges and Opportunities in Interactive Multi-Agentic Systems. \textit{13th International Conference of Human Agent Interaction (HAI'25)}.

    \item Yu, Y., Zhang, Y., \textbf{Johal, W.}, \& Burnett, G. (2025). Exploring deictic interface referencing outside-vehicle landmarks: Study of in-cabin multimodal interaction. \textit{Adjunct Proceedings of the 17th International Conference on Automotive User Interfaces and Interactive Vehicular Applications}.

    \item Zhang, J., Buckingham, G., \textbf{Johal, W.}, \& Knibbe, J. (2025). ThumbShift: Modulating Perceived Object Properties Through Dynamic Thumb Repositioning. \textit{2025 IEEE International Symposium on Mixed and Augmented Reality (ISMAR)}, pp.\ 571--581.

    \item Schömbs, S., Goncalves, J., \& \textbf{Johal, W.} (2025). ``I can feel the risks by looking at the robot face'': Communicating Risk through a Physical Agent. \textit{Proceedings of the Designing Interactive Systems Conference (DIS '25)}.

    \item Zhang, Y., Ratnayake, T.\ S., Sew, C., Knibbe, J., Goncalves, J., \& \textbf{Johal, W.} (2025). Can you pass that tool?: Implications of indirect speech in physical human-robot collaboration. \textit{Proceedings of the 2025 CHI Conference on Human Factors in Computing Systems}, pp.\ 1--18.

    \item Pan, J., Eden, J., Oetomo, D., \& \textbf{Johal, W.} (2025). Using Fitts' Law to Benchmark Assisted Human-Robot Performance. \textit{2025 20th ACM/IEEE International Conference on Human-Robot Interaction (HRI)}, pp.\ 203--212.

    \item Tabatabaei, R., Kostakos, V., \& \textbf{Johal, W.} (2025). Gazing at failure: Investigating human gaze in response to robot failure in collaborative tasks. \textit{2025 20th ACM/IEEE International Conference on Human-Robot Interaction (HRI)}.

    \item Pan, J., Schombs, S., Zhang, Y., Tabatabaei, R., Bilal, M., \& \textbf{Johal, W.} (2025). OfficeMate: Pilot Evaluation of an Office Assistant Robot. \textit{2025 20th ACM/IEEE International Conference on Human-Robot Interaction (HRI)}, pp.\ 1529--1533.

    \item Zhang, J., \textbf{Johal, W.}, \& Knibbe, J. (2025). Illusion Spaces in VR: The Interplay Between Size and Taper Angle Perception in Grasping. \textit{Proceedings of the 2025 CHI Conference on Human Factors in Computing Systems}, pp.\ 1--17.

    \item Tabatabaei, R., Kostakos, V., \& \textbf{Johal, W.} (2025). Real-Time Detection of Robot Failures Using Gaze Dynamics in Collaborative Tasks. \textit{2025 20th ACM/IEEE International Conference on Human-Robot Interaction (HRI)}, pp.\ 1660--1664.

    \item Golding, A., \textbf{Johal, W.}, \& Sammut, C. (2025). Person Tracking and Modelling for a Human Interaction Robot. \textit{2025 20th ACM/IEEE International Conference on Human-Robot Interaction (HRI)}, pp.\ 1309--1313.

    \item Zhang Y., Li H., Tabatabaei R., \& \textbf{Johal W.} (2025). ROSAnnotator: A Web Application for ROSBag Data Analysis in Human-Robot Interaction. \textit{Proceedings of the 2025 ACM/IEEE International Conference on Human-Robot Interaction (HRI '25)}, pp.\ 1099--1103.

    \item Zhou, Q., Chacon, A., Pan, J., \& \textbf{Johal, W.} (2025). Assisting MoCap-Based Teleoperation of Robot Arm using Augmented Reality Visualisations. \textit{Proceedings of the 2025 ACM/IEEE International Conference on Human-Robot Interaction (HRI '25)}.

    \item Chen J., Chacon A., Bilal M., Zhou Q., \& \textbf{Johal, W.} (2024). Mr.LfD: A Mixed Reality Interface for Robot Learning from Demonstration. \textit{Proceedings of the 36th Australian Conference on Human-Computer Interaction (OzCHI '24)}.

    \item Kelesbekov, U., Marini, G., Bai, Z., \textbf{Johal, W.}, Velloso, E., \& Knibbe, J. (2024). Stuet: Dual Stewart Platforms for Pinch Grasping Objects in VR. \textit{2024 IEEE International Symposium on Mixed and Augmented Reality (ISMAR)}, pp.\ 309--318.

    \item Bilal M., Lipovetzky N., Oetomo D., \& \textbf{Johal, W.} (2024). Beyond Success: Quantifying Demonstration Quality in Learning from Demonstration. \textit{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS 2024)}.

    \item Schömbs, S., Pan, J., Zhang, Y., Goncalves, J., \& \textbf{Johal, W.} (2024). FaceVis: Exploring a Robot's Face for Affective Visualisation Design. \textit{Extended Abstracts of the CHI Conference on Human Factors in Computing Systems (CHI '24)}, pp.\ 1--10.

    \item Schömbs S., Pareek S., Goncalves J., \textbf{Johal W.} (2024). Robot-Assisted Decision-Making: Unveiling the Role of Uncertainty Visualisation and Embodiment. \textit{Proceedings of the SIGCHI Conference on Human Factors in Computing Systems (CHI'24)}.

    \item Yu, X., Tran, T., Wang, Y., Mah, K., Cao, Y., Johansen, S., \textbf{Johal, W.}, Lupetti, M., Rose, M., Rittenbruch, M., Zsolczay, R., \& Hoggenmüller, M. (2024). Out of Place Robot in the Wild: Envisioning Urban Robot Contextual Adaptability Challenges Through a Design Probe. \textit{Extended Abstracts of the 2024 CHI Conference on Human Factors in Computing Systems}.

    \item Admoni, H., \textbf{Johal, W}., Szafir, D., \& Sandygulova, A. (2024). Designing an Introductory HRI Course. \textit{Companion of the 2024 ACM/IEEE International Conference on Human-Robot Interaction}, pp.\ 1302--1304.

    \item Yadollahi, E., Romeo, M., Dogan, F., \textbf{Johal, W.}, De Graaf, M., Levy-Tzedek, S., \& Leite, I. (2024). Explainability for Human-Robot Collaboration. \textit{Companion of the 2024 ACM/IEEE International Conference on Human-Robot Interaction}, pp.\ 1364--1366.

    \item Gamboa, M., Ljungblad, S., \textbf{Johal, W.}, Mubin, O., \& Obaid, M. (2023). Championing Design Knowledge in Human-Drone Interaction Research. \textit{Proceedings of the 11th International Conference on Human-Agent Interaction (HAI'23)}, pp.\ 365--368.

    \item Liu, C.\ Y., Mohammadi, G., Song, Y., \& \textbf{Johal, W.} (2023). Speech-Gesture GAN: Gesture Generation for Robots and Embodied Agents. \textit{32nd IEEE International Conference on Robot and Human Interactive Communication (RO-MAN'23)}, pp.\ 405--412.

    \item Phaijit, O., Sammut, C., \& \textbf{Johal, W.} (2023). User Interface Interventions for Improving Robot Learning from Demonstration. \textit{Proceedings of the 11th International Conference on Human-Agent Interaction (HAI'23)}, pp.\ 152--161.

    \item Tozadore, D.\ C., Nasir, J., Gillet, S., van den Berghe, R., Guneysu, A., \& \textbf{Johal, W}. (2023). Robots for Learning 7 (R4L) A Look from Stakeholders' Perspective. \textit{Companion of the 2023 ACM/IEEE International Conference on Human-Robot Interaction (HRI'23)}, pp.\ 935--937.

    \item Fourie, C., Figueroa, N., Shah, J., Bieńkiewicz, M., Bardy, B., Burdet, E., Singamaneni, P.\ T., Alami, R., Curioni, A., Knoblich, G., \textbf{Johal, W.}\ \& others. (2022). Joint Action, Adaptation, and Entrainment in Human-Robot Interaction. \textit{Proceedings of the 2022 ACM/IEEE International Conference on Human-Robot Interaction (HRI'22)}, pp.\ 1250--1253.

    \item Phaijit, O., Sammut, C., \& \textbf{Johal, W}. (2022). Let's Compete! The Influence of Human-Agent Competition and Collaboration on Agent Learning and Human Perception. \textit{Proceedings of the 10th International Conference on Human-Agent Interaction (HAI'22)}, pp.\ 86--94.

    \item Rakhymbayeva, N., Balgabekova, Z., Nurmukhamed, M., Burunchina, K., \textbf{Johal, W.}, \& Sandygulova, A. (2022). To Transfer or Not To Transfer: Engagement Recognition within Robot-Assisted Autism Therapy. \textit{Proceedings of the 2022 ACM/IEEE International Conference on Human-Robot Interaction (HRI'22)}, pp.\ 1002--1006.

    \item Phaijit, O., Obaid, M., Sammut, C., \& \textbf{Johal, W.} (2022). A Demonstration of the Taxonomy of Functional Augmented Reality for Human-Robot Interaction. \textit{2022 ACM/IEEE International Conference on Human-Robot Interaction (HRI)}, pp.\ 981--985.

    \item Obaid, M., Tatar, K., Wiberg, M., Said, A., Rost, M., Weilenmann, A., \textbf{Johal, W.}, \& Eyssel, F. (2022). Social Drones for Health and Well-being. \textit{Adjunct Proceedings of the 2022 Nordic Human-Computer Interaction Conference (NordiCHI'22)}, pp.\ 1--4.

    \item Phaijit, O., Obaid, M., Sammut, C., \& \textbf{Johal, W.} (2022). A Taxonomy of Functional Augmented Reality for Human-Robot Interaction. \textit{Proceedings of the 2022 ACM/IEEE International Conference on Human-Robot Interaction (HRI'22)}, pp.\ 294--303.

    \item Ingle, D., Marcus, N., \& \textbf{Johal, W.} (2021). The Valley of non-Distraction: Effect of Robot's Human-likeness on Perception Load. \textit{Companion of the 2021 ACM/IEEE International Conference on Human-Robot Interaction (HRI '21 Companion)}.

    \item \textbf{Johal, W.}, Bruno, B., Olsen, J.\ K., Chetouani, M., Lemaignan, S., \& Sandygulova, A. (2021). Robots for Learning -- Learner-Centred Design. \textit{Companion of the 2021 ACM/IEEE International Conference on Human-Robot Interaction (HRI '21 Companion)}, pp.\ 715--716.

    \item Liu, Y., Mohammadi, G., Song, Y., \& \textbf{Johal, W.} (2021). Speech-based Gesture Generation for Robots and Embodied Agents: A Scoping Review. \textit{Proceedings of the 9th International Conference on Human-Agent Interaction (HAI'21)}, pp.\ 31--38.

    \item Ioannou, C., Neophytou, C., Asselborn, T., \textbf{Johal, W.}, \& Hadzilacos, T. (2020). Learning (Good Handwriting in Greek) by Teaching (a Humanoid Robot). \textit{INTED'20 Proceedings}, pp.\ 7287--7296.

    \item Chibaudel, Q., \textbf{Johal, W.}, Oriola, B., J-M\ Macé, M., Dillenbourg, P., Tartas, V., \& Jouffrais, C. (2020). ``If You've Gone Straight, Now, You Must Turn Left'' -- Exploring the Use of a Tangible Interface in a Collaborative Treasure Hunt for People with Visual Impairments. \textit{The 22nd International ACM SIGACCESS Conference on Computers and Accessibility}.

    \item \textbf{Johal, W.}, Peng, Y., \& Mi, H. (2020). Swarm Robots in Education: A Review of Challenges and Opportunities. \textit{Proceedings of the 8th International Conference on Human-Agent Interaction (HAI'20)}, pp.\ 272--274.

    \item Khodr, H., Kianzad, S., \textbf{Johal, W.}, Kothiyal, A., Bruno, B., \& Dillenbourg, P. (2020). AlloHaptic: Robot-Mediated Haptic Collaboration for Learning Linear Functions. \textit{2020 29th IEEE International Conference on Robot and Human Interactive Communication (RO-MAN'20)}, pp.\ 27--34.

    \item Neto, I., \textbf{Johal, W.}, Couto, M., Nicolau, H., Paiva, A., \& Guneysu, A. (2020). Using Tabletop Robots to promote Inclusive Classroom Experiences. \textit{Proceedings of the 19th ACM Conference on Interaction Design and Children (IDC'20)}, pp.\ 281--292.

    \item Obaid, M., \textbf{Johal, W.}, \& Mubin, O. (2020). Domestic Drones: Context of Use in Research Literature. \textit{Proceedings of the 8th International Conference on Human-Agent Interaction (HAI'20)}, pp.\ 196--203.

    \item Sandygulova, A., \textbf{Johal, W.}, Zhexenova, Z., Tleubayev, B., Zhanatkyzy, A., Turarova, A., Telisheva, Z., CohenMiller, A., Asselborn, T., \& Dillenbourg, P. (2020). CoWriting Kazakh: Learning a New Script with a Robot. \textit{2020 ACM/IEEE International Conference on Human-Robot Interaction (HRI'20)}, pp.\ 113--120.

    \item Tleubayev, B., Zhexenova, Z., Asselborn, T., \textbf{Johal, W.}, Dillenbourg, P., \& Sandygulova, A. (2020). CoWriting Kazakh: Learning a New Script with a Robot -- Demonstration. \textit{Companion of the 2020 ACM/IEEE International Conference on Human-Robot Interaction (HRI'20 Companion)}, pp.\ 79--79.

    \item Yadollahi, E., Couto, M., \textbf{Johal, W.}, Dillenbourg, P., \& Paiva, A. (2020). Exploring the Role of Perspective Taking in Educational Child-Robot Interaction. \textit{International Conference on Artificial Intelligence in Education (AIED'20)}, pp.\ 346--351.

    \item Zhexenova, Z., Tleubayev, B., Zhanatkyzy, A., Turarova, A., Telisheva, Z., \textbf{Johal, W.}, Asselborn, T., Dillenbourg, P., \& Sandygulova, A. (2020). CoWriting Kazakh: Learning a New Script with a Robot -- Video. \textit{2020 ACM/IEEE International Conference on Human-Robot Interaction (HRI'20)}.

    \item El Hamamsy, L., \textbf{Johal, W.}, Asselborn, T., Nasir, J., \& Dillenbourg, P. (2019). Learning By Collaborative Teaching: An Engaging Multi-Party CoWriter Activity. \textit{2019 28th IEEE International Conference on Robot and Human Interactive Communication (RO-MAN'19)}, pp.\ 1--8.

    \item \textbf{Johal, W.}, Robu, O., Dame, A., Magnenat, S., \& Mondada, F. (2019). Augmented Robotics for Learners: A Case Study on Optics. \textit{2019 28th IEEE International Conference on Robot and Human Interactive Communication (RO-MAN'19)}, pp.\ 1--6.

    \item \textbf{Johal, W.,} Sandygulova, A., De Wit, J., De Haas, M., \& Scassellati, B. (2019). Robots for Learning -- R4L: Adaptive Learning. \textit{2019 14th ACM/IEEE International Conference on Human-Robot Interaction (HRI'19)}, pp.\ 693--694.

    \item \textbf{Johal, W.}, Tran, A., Khodr, H., Özgür, A., \& Dillenbourg, P. (2019). TIP: Tangible e-Ink Paper Manipulatives for Classroom Orchestration. \textit{Proceedings of the 31st Australian Conference on Human-Computer-Interaction (OzCHI'19)}, pp.\ 595--598.

    \item \textbf{Johal W.}, Andersen S., Chevalier M., Mondada F.\ \& Dillenbourg P. Learning Symmetry with Tangible Robots. \textit{Conference on Robots in Education (RiE)}, Vienna, Austria, April 2019.

    \item Kim, A., Omarova, M., Zhaksylyk, A., Asselborn, T., \textbf{Johal, W.}, Dillenbourg, P., \& Sandygulova, A. (2019). CoWriting Kazakh: Transitioning to a New Latin Script using Social Robots. \textit{28th IEEE International Conference on Robot and Human Interactive Communication (RO-MAN'19)}, pp.\ 1--6.

    \item Nasir, J., Norman, U., \textbf{Johal, W.}, Olsen, J.\ K., Shahmoradi, S., \& Dillenbourg, P. (2019). Robot Analytics: What Do Human-Robot Interaction Traces Tell Us About Learning? \textit{28th IEEE International Conference on Robot and Human Interactive Communication (RO-MAN'19)}.

    \item Ozgur, A.\ G., Faucon, L.\ P., Maceira-Elvira, P., Wessel, M.\ J., \textbf{Johal, W.}, Özgür, A., Cadic-Melchior, A., Hummel, F.\ C., \& Dillenbourg, P. (2019). Towards an Adaptive Upper Limb Rehabilitation Game with Tangible Robots. \textit{IEEE 16th International Conference on Rehabilitation Robotics (ICORR'19)}, pp.\ 294--299.

    \item Ozgur, A.\ G., Wessel, M.\ J., Asselborn, T., Olsen, J.\ K., \textbf{Johal, W.}, Ozgur, A., Hummel, F.\ C., \& Dillenbourg, P. (2019). Designing Configurable Arm Rehabilitation Games: How Do Different Game Elements Affect User Motion Trajectories? \textit{41st Annual International Conference of the IEEE Engineering in Medicine and Biology Society (EMBC'19)}

    \item Sandygulova, A., CohenMiller, A., Oralbayeva, N., \textbf{Johal, W.}, Asselborn, T., \& Dillenbourg, P. (2019). Cognitive Learning with a Robot: The Case of Script Acquisition. \textit{International Conference on Software Engineering and Formal Methods}, pp.\ 154--162.

    \item Shahmoradi, S., Olsen, J.\ K., Haklev, S., \textbf{Johal, W.}, Norman, U., Nasir, J., \& Dillenbourg, P. (2019). Orchestration of Robotic Activities in Classrooms: Challenges and Opportunities. \textit{European Conference on Technology Enhanced Learning (ECTEL'19)}, pp.\ 640--644.

    \item Yadollahi, E., \textbf{Johal, W}., Dias, J., Dillenbourg, P., \& Paiva, A. (2019). Studying the Effect of Robot Frustration on Children's Change of Perspective. \textit{2019 8th International Conference on Affective Computing and Intelligent Interaction Workshops and Demos (ACIIW'19)}, pp.\ 381--387.

    \item Charisi V., Alcorn A.M., Kennedy J., \textbf{Johal W.}, Baxter P., Kynigos C. The near future of children's robotics. \textit{Proceedings of the 17th ACM Conference on Interaction Design and Children (IDC'18)}.

    \item Yadollahi E., \textbf{Johal W.}, Paiva A.\ \& Dillenbourg P. When Deictic Gestures in a Robot Can Harm Child-Robot Collaboration. \textit{ACM Interaction Design and Children (IDC'18) Conference, 2018}. \faTrophy

    \item Asselborn T., Guneysu A., Mrini K., Yadollahi E., \textbf{Johal W.}, Ozgur A.\ \& Dillenbourg P. Bringing Letters to Life: Writing with Haptic-Enabled Tangible Robots. \textit{ACM Interaction Design and Children (IDC) Conference, 2018}.

    \item Guneysu A., Wessel M., \textbf{Johal W.}, Sharma K., Özgür A., Vuadens P., Mondada F., Hummel F., and Dillenbourg P. Iterative Design of an Upper Limb Rehabilitation Game with Tangible Robots. \textit{Proceedings of the 2018 ACM/IEEE International Conference on Human-Robot Interaction}.

    \item Asselborn, T., \textbf{Johal, W.}, \& Dillenbourg, P. Keep on Moving! Exploring Anthropomorphic Effects of Motion during Idle Moments. \textit{26th IEEE International Symposium on Robot and Human Interactive Communication (RO-MAN), 2018}.

    \item Ozgur A., \textbf{Johal W.}, Mondada F.\ and Dillenbourg P. Haptic-Enabled Handheld Mobile Robots: Design and Analysis. \textit{ACM CHI Conference on Human Factors in Computing Systems (CHI)}, 2017.

    \item \textbf{Johal W.}, Vogt P., Kennedy J., De Haas M., Paiva A., Castellano G., Okita S., Tanaka F., Belpaeme T., Dillenbourg P. Workshop on Robots for Learning: R4L. \textit{ACM/IEEE International Conference on Human-Robot Interaction (HRI)}, 2017.

    \item Özgür A., \textbf{Johal W.}, Mondada F and Dillenbourg P. Windfield: Learning Wind Meteorology with Handheld Haptic Robots. \textit{ACM/IEEE International Conference on Human-Robot Interaction (HRI)}, 2017.

    \item Özgür A., \textbf{Johal W.}, Mondada F and Dillenbourg P. Windfield: Demonstrating Wind Meteorology with Handheld Haptic Robots. \textit{ACM/IEEE International Conference on Human-Robot Interaction (HRI)}, 2017.

    \item Ozgur A., Lemaignan S., \textbf{Johal W.}, Mondada F.\ and Dillenbourg P. Cellulo: Versatile Handheld Robots for Education. \textit{ACM/IEEE International Conference on Human-Robot Interaction (HRI)}, 2017. \faTrophy

    \item Adam C., \textbf{Johal W.}, Pellier D., Fiorino H.\ and Pesty S. Social Human-Robot Interaction: A New Cognitive and Affective Interaction-Oriented Architecture. \textit{International Conference on Social Robotics (ICSR)}, 2016.

    \item Özgür A., \textbf{Johal W.}\ and Dillenbourg P. Permanent Magnet-Assisted Omnidirectional Ball Drive. \textit{International Conference on Intelligent Robots and Systems (IROS)}, 2016.

    \item \textbf{Johal W.}, Jacq A., Paiva A.\ and Dillenbourg P. Child-Robot Spatial Arrangement in a Learning by Teaching Activity. \textit{25th IEEE International Symposium on Robot and Human Interactive Communication}, August 2016, New York, USA.

    \item Ta V.C., \textbf{Johal W}., Portaz M., Castelli E., Vaufreydaz D. The Grenoble system for the Social Touch Challenge at ICMI 2015. \textit{International Conference on Multimodal Interaction (ICMI2015)}. \faTrophy

    \item \textbf{Johal W}., Calvary G., Pesty S. Non-verbal Signals in HRI: Interference in Human Perception. \textit{International Conference on Social Robotics (ICSR2015)}.

    \item \textbf{Johal W.}, Pellier D., Adam C., Fiorino H., Pesty S. A Cognitive and Affective Architecture for Social Human-Robot Interaction. \textit{Proceedings of the ACM International Conference in Human Robot Interaction (HRI'15)}. \faTrophy

    \item \textbf{Johal W.} Robots Interacting with Style. \textit{Proceedings of the ACM International Conference in Human Robot Interaction (HRI'15)}.

    \item \textbf{Johal W.}, Calvary G., Pesty S. Toward Companion Robots Behaving with Style. \textit{Proceedings of the 2014 IEEE International Symposium on Robot and Human Interactive Communication (ROMAN)}, Edinburgh, 2014.

    \item \textbf{Johal W.}, Adam C., Fiorino H., Pesty, S., Duhaut D. Acceptability of a companion robot for children in daily life situations. \textit{5th IEEE Conference on Cognitive InfoCommunications (CogInfoCom)}, Nov 2014, Vietri, Italy.

    \item \textbf{Johal W.}, Calvary G.\ and Pesty S. A Robot with Style because you are Worth it! \textit{CHI '14 Extended Abstracts on Human Factors in Computing Systems (CHI EA '14)}, Toronto, Canada.

    \item \textbf{Johal W.}, Dugdale J., Pesty S. Modelling interactions in a mixed agent world. \textit{Proceedings of 25th European Modeling and Simulation Symposium (EMSS)}, Athens, Greece, 23--25 Sept 2013.

    \item \textbf{Benkaouar (Johal) W.}, Vaufreydaz D. Multi-sensors engagement detection with a robot companion in a home environment. \textit{Workshop on Assistance and Service Robotics in a Human Environment at IEEE IROS 2012}, Vilamoura, Algarve -- Portugal, Oct 2012.
\end{itemize}

\vspace{0.1in}

% ---- Book Chapters ----
\subsection{BOOK CHAPTERS}
\vspace{2pt}

\begin{itemize}[nosep]
    \renewcommand\labelitemi{$\bullet$}
    \item Bruno, B., Amirova, A., Sandygulova, A., Lugrin, B., \& \textbf{Johal, W.} (2023). Culture in Social Robots for Education. In \textit{Cultural Robotics: Social Robots and Their Emergent Cultural Ecologies} (pp.\ 127--145). Springer International Publishing Cham.

    \item Burget, L., Wang, C., Asselborn, T., Tozadore, D., \textbf{Johal, W.}, Gargot, T., Sandygulova, A., Kidziński, L., Cohen, D., \& Dillenbourg, P. (2023). Handwriting Analytics. In \textit{Routledge International Handbook of Visual-motor skills, Handwriting, and Spelling} (pp.\ 412--425). Routledge.
\end{itemize}

\vspace{0.1in}

% ---- Peer-reviewed French Conference Publications ----
\subsection{PEER-REVIEWED FRENCH CONFERENCE PUBLICATIONS}
\vspace{2pt}

\begin{itemize}[nosep]
    \renewcommand\labelitemi{$\bullet$}
    \item \textbf{Johal W.}, Özgür A., Mondada F and Dillenbourg P. Projet Cellulo. \textit{Conference IHM (IHM2016)}, Fribourg, 2016.

    \item Jacq A., \textbf{Johal W}.\ and Dillenbourg P. Non-recursive Approach for Mutual Understanding. \textit{Journée de travail sur la robotique interactive et cognitive}, Avril 2016, Toulouse, France.

    \item \textbf{Johal W.}, Pesty, S., Calvary G. Des Styles pour une Personnalisation de l'Interaction Homme-Robot. \textit{Journées Nationales de la Robotique Interactive (JNRI)}, Nov.\ 2014, Toulouse, France.

    \item \textbf{Johal W.}, Pesty S.\ Calvary G. Les Styles pour la Plasticité des Robots Compagnons. \textit{Workshop Affect, Compagnon Artificiel, Interaction (WACAI) 2014}, Rouen, France.

    \item Adam C., \textbf{Johal W.}, Ben-Farhat I., Jost C., Fiorono H., Pesty S., Duhaut D. Acceptabilité d'un robot compagnon dans des situations de la vie quotidienne. \textit{Deuxième conférence III -- Intercompréhension de l'intraspécifique à l'interspécifique}, Lorient, 30 Sept -- 1 Oct 2013.
\end{itemize}

\vspace{0.1in}

% ---- International Patents ----
\subsection{INTERNATIONAL PATENTS}
\vspace{2pt}

\begin{itemize}[nosep]
    \renewcommand\labelitemi{$\bullet$}
    \item Özgür A., Lemaignan S., \textbf{Johal W.}, Mondada F.\ and Dillenbourg P. ``Magnet Assisted Ball-Drive.'' U.S.\ Patent US15/648,425, applied July 12, 2017.
    \item Asselborn T., Zolna K., \textbf{Johal W.}\ and Dillenbourg P. ``Character Recognition Confirmation.'' International Patent PCT/EP2017/080430, applied November 24, 2017.
    \item Zolna K., Asselborn T., \textbf{Johal W.} Method of handwritten character recognition confirmation. US Patent 11,164,025, November 2021.
\end{itemize}

\vspace{0.1in}

% ---- Other Contributions ----
\subsection{OTHER CONTRIBUTIONS}
\vspace{2pt}

\begin{itemize}[nosep]
    \renewcommand\labelitemi{$\bullet$}
    \item Volodin, S., Khodr, H., Dillenbourg, P., \& \textbf{Johal, W.} (2025). Going Down the Abstraction Stream with Augmented Reality and Tangible Robots: the Case of Vector Instruction. \textit{arXiv preprint arXiv:2504.14562}.

    \item Schömbs, S., Goncalves, J., \& \textbf{Johal, W.} (2024). Exploring Data Agency and Autonomous Agents as Embodied Data Visualizations. \textit{arXiv preprint arXiv:2402.04598}.

    \item \textbf{Johal, W.} Transferability of HRI Research: Potential and Challenges. \textit{AAAI Spring Symposium on Industry and HRI}, (April 2023), Palo Alto, USA.

    \item Guneysu, A., \textbf{Johal, W.}, Ozgur, A., \& Dillenbourg, P. (2018). Tangible Robots Mediated Collaborative Rehabilitation Design: Can we Find Inspiration from Scripting Collaborative Learning? \textit{Robots for Learning Workshop on Inclusive Learning}.

    \item Jacq A., \textbf{Johal W.}, Dillenbourg P.\ and Paiva A. Cognitive Architecture for Mutual Modelling. \textit{Workshop on Cognitive Architectures for Social HRI (HRI'16)}, Christchurch, New Zealand, 2016.

    \item \textbf{Johal W.}, Pesty S., Calvary G. Expressing Parenting Styles with Companion Robots. \textit{Workshop on Applications for Emotional Robots at Human-Robot Interaction conference (HRI'14)}, Bielefeld, 2014.
\end{itemize}

\vspace{0.1in}

% ---- Thesis ----
\subsection{THESIS}
\vspace{2pt}

\begin{itemize}[nosep]
    \renewcommand\labelitemi{$\bullet$}
    \item \textbf{Johal, W.} Companion Robots Behaving with Style: Towards Plasticity in Social Human-Robot Interaction. \textit{PhD in Computer Sciences, Université Grenoble Alpes}, Prof.\ Pesty S and Calvary G. (June 2016).
    \item \textbf{Benkaouar (Johal) W.} Detection of non-verbal communication cues using multi-modal sensors: engagement detection. \textit{Master Thesis in Computer Sciences}, under the supervision of Dominique Vaufreydaz, Team PRIMA -- INRIA Rhônes-Alpes, Université Joseph Fourier, Grenoble -- France, (June 2012).
\end{itemize}
