% ============================================================
% PUBLICATIONS — top 10 (numbered list)
% Source: publications_top10.tex (deprecated) — section extracted
%         from that standalone document.
% ============================================================

\subsection{SELECTED LIST OF PUBLICATIONS}
\vspace{2pt}

\begin{enumerate}[nosep]
    \item \textbf{Johal, W.} (2020). Research trends in social robots for learning. \textit{Current Robotics Reports}, 1(3), 75--83.
    \item Bruno, B., Amirova, A., Sandygulova, A., Lugrin, B., \& \textbf{Johal, W.} (2023). Culture in social robots for education. In \textit{Cultural Robotics: Social Robots and Their Emergent Cultural Ecologies} (pp.\ 127--145). Cham: Springer International Publishing.
    \item Gargot, T., Asselborn, T., Zammouri, I., Brunelle, J., \textbf{Johal, W.}, Dillenbourg, P., Cohen D.\ \& Anzalone, S.\ M. (2021). ``It Is Not the Robot Who Learns, It Is Me.'' Treating Severe Dysgraphia Using Child--Robot Interaction. \textit{Frontiers in Psychiatry}, 12, 596055.
    \item Guneysu Ozgur, A., Wessel, M.\ J., \textbf{Johal, W.}, Sharma, K., Özgür, A., Vuadens, P., \& Dillenbourg, P. (2018, February). Iterative design of an upper limb rehabilitation game with tangible robots. In \textit{Proceedings of the 2018 ACM/IEEE International Conference on Human-Robot Interaction} (pp.\ 241--250).
    \item Olsen, J.\ K., Ozgur, A.\ G., Sharma, K., \& \textbf{Johal, W.} (2022). Leveraging eye tracking to understand children's attention during game-based, tangible robotics activities. \textit{International Journal of Child-Computer Interaction}, 31, 100447.
    \item Gargot, T., Archambault, D., Chetouani, M., Cohen, D., \textbf{Johal, W.}, \& Anzalone, S.\ M. (2022). Automatic assessment of motor impairments in autism spectrum disorders: A systematic review. \textit{Cognitive Computation}, 14(2), 624--659.
    \item Amirova, A., Rakhymbayeva, N., Yadollahi, E., Sandygulova, A., \& \textbf{Johal, W.} (2021). 10 years of human-NAO interaction research: A scoping review. \textit{Frontiers in Robotics and AI}, 8, 744526.
    \item Guneysu Ozgur, A., Wessel, M.\ J., Olsen, J.\ K., \textbf{Johal, W.}, Ozgur, A., Hummel, F.\ C., \& Dillenbourg, P. (2020). Gamified motor training with tangible robots in older adults: a feasibility study and comparison with the young. \textit{Frontiers in Aging Neuroscience}, 12, 59.
    \item Özgür, A., \textbf{Johal, W.}, Mondada, F., \& Dillenbourg, P. (2017, May). Haptic-enabled handheld mobile robots: Design and analysis. In \textit{Proceedings of the 2017 CHI Conference on Human Factors in Computing Systems} (pp.\ 2449--2461).
    \item Ta, V.\ C., \textbf{Johal, W.}, Portaz, M., Castelli, E., \& Vaufreydaz, D. (2015, November). The Grenoble system for the social touch challenge at ICMI 2015. In \textit{Proceedings of the 2015 ACM on International Conference on Multimodal Interaction} (pp.\ 391--398).
\end{enumerate}
