% ============================================================
% PUBLICATIONS — mini (5 selected recent entries)
% Source: section_publication_mini.tex (deprecated)
% ============================================================

\subsection{SELECTED RECENT PUBLICATIONS}
\vspace{2pt}

{\small
\begin{itemize}[nosep]

    \item Bilal, M., Ratnayake, T. S., Chacon, D. A., Lipovetzky, N., Oetomo, D., \& \textbf{Johal, W.} (2026). Design and evaluation of AR-based real-time feedback system for kinesthetic robot teaching. In Proceedings of the Designing Interactive Systems Conference (DIS '26). ACM. https://doi.org/10.1145/3800645.3812951 \faMedal

    \item Tabatabaei, R., Kostakos, V., \& \textbf{Johal, W.} (2026). Oops, I Did It Again (But I Know It): Robot Failure Consistency and Awareness in Human-Robot Collaboration. \textit{Proceedings of the 2026 CHI Conference on Human Factors in Computing Systems}. ACM. \faMedal

    
    \item Schömbs, S., Zhang, Y., Goncalves, J., \& \textbf{Johal, W.} (2025). From Conversation to Orchestration: HCI Challenges and Opportunities in Interactive Multi-Agentic Systems. \textit{arXiv preprint arXiv:2506.20091}.

    \item Schömbs, S., Goncalves, J., \& \textbf{Johal, W.} (2025). ``I can feel the risks by looking at the robot face'': Communicating risk through a physical agent. In \textit{Proceedings of the 2025 ACM Designing Interactive Systems Conference (DIS '25)} (pp.\ 236--252). Association for Computing Machinery.

    \item Zhang, Y., Ratnayake, T.\ S., Sew, C., Knibbe, J., Goncalves, J., \& \textbf{Johal, W.} (2025, April). Can you pass that tool?: Implications of indirect speech in physical human-robot collaboration. In \textit{Proceedings of the 2025 CHI Conference on Human Factors in Computing Systems} (pp.\ 1--18).

    \item Pan, J., Eden, J., Oetomo, D., \& \textbf{Johal, W.} (2024). Effects of Shared Control on Cognitive Load and Trust in Teleoperated Trajectory Tracking. \textit{IEEE Robotics and Automation Letters}, 9(6), 5863--5870.

    \item Tabatabaei, R., Kostakos, V., \& \textbf{Johal, W.} (2025, March). Gazing at failure: Investigating human gaze in response to robot failure in collaborative tasks. In \textit{2025 20th ACM/IEEE International Conference on Human-Robot Interaction (HRI)} (pp.\ 939--948). IEEE.

    \item Schömbs S., Pareek S., Goncalves J., \textbf{Johal W.} (2024). Robot-Assisted Decision-Making: Unveiling the Role of Uncertainty Visualisation and Embodiment. \textit{Proceedings of the SIGCHI Conference on Human Factors in Computing Systems (CHI'24)}.
\end{itemize}
}
