% ============================================================
% SERVICE — conference/workshop organisation + scientific societies
% Sources merged:
%   section_conf_organization.tex  (14 workshop/seminar entries)
%   Commented-out Professional Associations block from section_membership.tex
% ============================================================

\subsection{RESEARCH WORKSHOPS AND SEMINARS ORGANISATION}
\vspace{2pt}

\begin{itemize}
    \item ``Human-Robot Interaction for Explainability in Robotics'' @Ro-Man 2023, \href{https://sites.google.com/view/x-hri/all-workshops/roman2023?authuser=0}{X-HRI@RoMan2023}. Hybrid -- August 2023, Busan.
    \item ``Workshop on Robots for Learning -- AI to Power Robots'' @Ro-Man 2023, \href{https://robots4learning.wordpress.com/r4lroman2023/}{R4L@RoMan2023}. Hybrid -- August 2023, Busan.
    \item ``Workshop on Joint Action, Adaptation, and Entrainment in Human-robot interaction'' @HRI 2022. Virtual -- March 8, 2022.
    \item ``Workshop on Robots for Learning -- Learner Centred Design'' @HRI 2021, \href{https://robot4learning.github.io/event/hri2021/}{R4L@HRI2021}. Virtual -- March 12, 2021.
    \item ``Workshop on Robots for Learning -- Building Robots for Classroom Context'' @RoMan 2019, \href{https://robots4learning.wordpress.com/r4lroman2019/}{R4L@ROMAN2019}. New Delhi, India -- October 14, 2019.
    \item ``Workshop on Robots for Learning -- Adaptive Learning'' @HRI 2019, \href{http://r4l.epfl.ch/HRI2019}{R4L@HRI2019}. Daegu, South Korea -- March 11, 2019.
    \item Winter School on ``Developing Technologies in Educational Settings'', \href{https://www.epfl.ch/labs/chili/index-html/research/animatas/digital-learning-ws/}{EPFL}, Switzerland -- Feb 4--8, 2019.
    \item ``Workshop on the Near Future of Child Robot Interaction'' @IDC 2018, \href{https://sites.google.com/view/cri-idc-workshop}{CRI@IDC}. Trondheim, Norway -- June 20, 2018.
    \item ``Workshop on Robots for Learning -- Inclusive Learning'' @HRI 2018, \href{http://r4l.epfl.ch/HRI2018}{R4L@HRI2018}. Chicago, IL, USA -- March 5, 2018.
    \item ``Workshop on Robots for Learning'' @HRI 2017, \href{http://r4l.epfl.ch/HRI2017}{R4L@HRI}. Vienna, Austria -- March 6, 2017.
    \item ``Workshop on Robots for Learning'' @RoMan 2016, \href{http://r4l.epfl.ch/}{R4L}. New York, USA -- August 27, 2016.
    \item ``Workshop on Social Robots in Education'', \href{https://socialrobotsineducation.wordpress.com/}{@NewFriends 2016}. Barcelona, Spain -- November 2, 2016.
    \item ``Workshop Affect, Compagnon Artificiel, Interaction'', \href{http://wacai2012.imag.fr/}{WACAI 2012}. Grenoble, France -- 15 \& 16 November 2012.
    \item \href{http://persycup.imag.fr/}{PersyCup Robotic Challenge}. Grenoble, France -- 21 May 2015.
\end{itemize}

% ---- Scientific Societies / Professional Associations ----
% (was commented out in original section_membership.tex:)
%\subsection{PROFESSIONAL ASSOCIATIONS}
%\vspace{2pt}
%\begin{itemize}
%    \item LEARN -- EPFL Center for Learning Sciences \href{https://learn.epfl.ch/}{}  % (was commented out in original)
%    \item NCCR Robotics, SNSF, Switzerland \href{https://nccr-robotics.ch/}{}  % (was commented out in original)
%    % IEEE Member  % (was commented out in original)
%    % RAS Member  % (was commented out in original)
%    % Co-founder of the Robodoc-LIG research group for PhD students at the Laboratory of Informatics of Grenoble.  % (was commented out in original)
%\end{itemize}
