% ============================================================
% INVITED TALKS — short (10 selected entries)
% Source: section_invited_talks_short.tex (deprecated)
% Commented-out entry from original is preserved below.
% ============================================================

\subsection{SELECTION OF INVITED TALKS}
\vspace{2pt}

\begin{itemize}
    \item Empowering Non-Technical Users: Training, Collaborating and Communicating with Robots, CSIRO, Australia, July 2024
    \item Robot-Assisted Decision Making: The risk for robot to convey utility instead of likelihood, Furhat Conference, Sweden, May 2024
    \item Human-Robot Interaction for Co-Learning, Canva, Sydney, Australia, September 2023
    \item Robots for co-learning. Monash University, Victoria, Australia, June 2022.
    \item Robots for learning but not robotics. Australasian Conference on Robotics and Automation (ACRA 2021), December 2021.
    \item Robots for Learning. Tsinghua University, China, November 2021, November 2023
    \item Assistive Human-Robot Interaction: From Education to Re-Education. ETH Zurich, Switzerland, Dec.\ 2018.
    \item Tangible Human-Robot Interaction: From Learning to Re-Learning, BioX Lab -- Stanford, Palo Alto, CA, USA. Nov.\ 2018.
    \item \href{https://www.swissnexboston.org/event/the-classroom-of-tomorrow-swarm-robots-in-education/}{The Classroom of Tomorrow -- Swarm Robots in Education}, Swissnex Boston, USA, April 2016.
    \item Non-verbal Communication in Human Robot Interaction, MIT Media Lab, Personal Robotics Group, April 2016.
    \item Engagement \& adaptation: How human-robot interaction can help in everyday life, Naver Labs Europe, December 2016.
\end{itemize}

% (was commented out in original:)
%\item Enabling smooth and personalized user-robot interaction to enhance learning, University of New South Wales, Sydney, Australia. Nov. 2018.  % (was commented out in original)
