% ============================================================
% INVITED TALKS — full (24 entries)
% Source: section_scientific_societies.tex (deprecated)
% Note: the source file was misleadingly named; its content is invited talks.
% ============================================================

\subsection{INVITED TALKS}
\vspace{2pt}

\begin{itemize}
    \item Empowering Novice Users to Train and Collaborate with Robots, LMU, Munich, Germany, July 2025
    \item Empowering Non-Technical Users: Training, Collaborating and Communicating with Robots, CSIRO, CINTEC, Australia, July 2024
    \item Robot-Assisted Decision Making: The risk for social robot to convey utility instead of likelihood, Furhat Conference, Sweden, May 2024
    \item Robots for Learning. Tsinghua University, China, December 2023
    \item Human-Robot Interaction for Co-Learning, Canva, Sydney, Australia, September 2023
    \item Robots for co-learning. Monash University, Victoria, Australia, June 2022.
    \item Robots for learning but not robotics. Invited Keynote Speaker at the Australasian Conference on Robotics and Automation (ACRA 2021), December 2021.
    \item Robots for Learning. Tsinghua University, China, November 2021
    \item Let's talk robotics, online podcast, Exaptec. May 2021.
    \item Social (Flying) Robots for Education. EduDrone Conference. September 2020.
    \item Orchestration of robot-populated classrooms. UC San Diego, California, USA. November 2019.
    \item Robots in Education. Swiss Technology Assessment Foundation. Focus group on Robotics. Bern, Switzerland, May 2019.
    \item From diagnosis to adaptive learning: CoWriter and Dysgraphia. Applied Machine Learning Days, Lausanne, Switzerland, January 2019.
    \item Robots for Learning. University of Nazerbachev, Astana, Kazakhstan, January 2019.
    \item Assistive Human-Robot Interaction: From Education to Re-Education. ETH Zurich, Switzerland, Dec.\ 2018.
    \item Teacher symposium on Computational Thinking, Entre-Deux-Lacs, HEPL, Yverdon-les-bains, Switzerland, Nov.\ 2018.
    \item \href{https://hri2019symposium.wordpress.com/}{HRI 2019 Mini symposium}, Stanford University, Palo Alto, CA, USA. Nov.\ 2018.
    \item Tangible Human-Robot Interaction: From Learning to Re-Learning, BioX Lab -- Stanford, Palo Alto, CA, USA. Nov.\ 2018.
    \item Enabling smooth and personalized user-robot interaction to enhance learning, University of New South Wales, Sydney, Australia. Nov.\ 2018.
    \item \href{http://laral.istc.cnr.it/swarm_robotics_2018/}{Swarm Robotics -- Pushing the state of the art}, Rome, Italy, Oct.\ 2018.
    \item \href{https://hri2018symposium.wordpress.com/}{HRI 2018 Mini symposium}, Cornell University, Ithaca, NY, USA. Nov.\ 2017.
    \item \href{https://www.swissnexboston.org/event/the-classroom-of-tomorrow-swarm-robots-in-education/}{The Classroom of Tomorrow -- Swarm Robots in Education}, Swissnex Boston, USA, April 2016.
    \item Non-verbal Communication in Human Robot Interaction, MIT Media Lab, Personal Robotics Group, April 2016.
    \item Engagement \& adaptation: How human-robot interaction can help in everyday life, Naver Labs Europe, December 2016.
\end{itemize}
